---
title: "Interactive Map"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-libraries, include=FALSE}
library(leaflet)
library(dplyr)
```

# What is this page about?
This page is about creating an interactive map using the leaflet package in R.
<br> We create an interacive map showing all the capitals of the countries in the world.

# Code
Here's the r code to create an interactive map
```{r}
country_data <- read.csv("countryCapital.csv")

map <- leaflet(country_data) %>%
  addTiles() %>%
  addCircleMarkers(
    ~Longitude, ~Latitude,
    label = ~paste(Capital.City),
    popup = ~paste("Country: ", Country, "<br>", "Capital: ", Capital.City),
    radius = 5,
    color = "blue",
    fillOpacity = 0.7
  )
```

# Map
Here's the final interactive map. Click on a blue dot formore details.
```{r}
map
```

# Data
- The data of the countries and their capitals can be found [here](https://gist.github.com/ofou/df09a6834a8421b4f376c875194915c9)
- The code is hosted at [this github repository](https://github.com/InfinityAkshay/R_Markdown_Leaflet)
